RadLib: a radiative heat transfer model library for CFD

### 2020-12-15 manuscript/manuscript.tex
Introduction edits (see DOL email 12/9/20)

Modeling radiative heat transfer, and particular radiation absorption coefficients, for CFD is complex and challenging. More specifically, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to simulation cost. As a result, researchers typically manufacture configurations in which radiation can be safely ignored, which can lead to results inapplicable to practical systems, or use oversimplified models and assumptions, which can produce inaccurate results. Unfortunately, these approaches are neither rigorous nor applicable to real engineering systems.

In some cases, other modes of heat transfer dominate the system, and radiation can be safely neglected, but many practical engineering systems do not allow this. Simple jet flames, for example, demonstrate both possibilities: early in a flame's development, convection typically dominates heat transfer and dictates flame behavior; late-stage flame phenomena like soot behavior and flame sheet breakthrough, however, increasingly depend on the magnitude of radiative heat losses and cannot be simulated accurately without a radiation model.

Like combustion, the core mechanisms of radiation are physically and mathematically complex. Unlike other modes of heat transfer, it is governed by a set of integro-differential equations that depend on both direction and wavelength. Only the simplest systems have analytic solutions, and most practical systems require a numerical solution. Ray tracing (Monte Carlo) solutions are very accurate but extremely computationally expensive, and often require high-performance computing resources to execute. Modeling assumptions are common and can reduce simulation cost at the expense of accuracy, depending on their validity for the system in question.

Currently, there is no convenient or easy-to-use access point for CFD radiation models. As such, we present RadLib, a modular library of radiation models that can be applied alongside various simulation tools. RadLib focuses on calculation of radiation absorption coefficients, often the most difficult and time-consuming portion of radiation calculations, which permits its use with various solvers. The models are fully implemented and validated and all use a common interface, allowing researchers easy and convenient access to radiation modeling tools regardless of the field of application.

>>>>

Modeling radiative heat transfer, and particular radiation absorption coefficients, for CFD is complex and challenging. More specifically, combustion simulations, which can require many complex property models already, are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to simulation cost. This can lead to simulations that use oversimplified radiation models, but in cases where radiation is significant relative to the other physical phenomena, oversimplified models can negatively impact the accuracy of simulation results. In some cases, radiative gains or losses are small compared to other sources, sinks, or modes of heat transfer, and radiation can be safely neglected, but many practical engineering systems do not allow this. For example, simple jet flames demonstrate both possibilities: early in a flame's development, turbulent mixing typically dominates heat transfer and dictates flame behavior; late-stage flame phenomena like soot behavior and flame sheet breakthrough, however, increasingly depend on the magnitude of radiative heat losses and are difficult to simulate accurately without a robust radiation model. These problems motivated development of the RadLib library, which provides a framework and uniform interface for radiation property models and implements three powerful models in C++ and Python, giving researchers easier and more convenient access to advanced radiation property models and a consistent framework for further model development.

The core mechanisms of radiative phenomena are physically and mathematically complex. Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE). Solving the RTE for a given system also requires information about the radiative properties of the materials and media involved, typically radiation absorption coefficients. Depending on the model, absorption coefficients can be dependent on a number of local system properties such as temperature, pressure, and gas composition. As a result, computational radiation solvers require two parts: first, a solution approach for the radiative transfer equations (RTE); and second, a radiation property model. RadLib addresses the second part by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.

%Like combustion, the core mechanisms of radiation are physically and mathematically complex. Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength. Only the simplest systems have analytic solutions, and most practical systems require a numerical solution. Ray tracing solutions are very accurate but extremely computationally expensive, and often require high-performance computing resources to execute. Modeling assumptions are common and can reduce simulation cost at the expense of accuracy, depending on their validity for the system in question.

With RadLib, we provide a convenient, easy-to-use access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications. RadLib is a modular C++ library with an optional Python interface used to compute the radiation properties of participating media, often the most difficult and time-consuming portion of radiation calculations. RadLib's current focus is calculating radiation absorption coefficients and weighting factors for use in global radiation models, but the flexible framework permits expansion to other radiative properties. Three models are fully implemented and validated and all use a common interface, allowing researchers easy and convenient access to radiation modeling tools regardless of the field of application.
